---
title: "Reproducibility example: pumpkins"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(ggplot2)
library(dplyr)
```

## Introduction

Write some text here about what you are doing. Show the code for reading in the `pumpkins.csv` file.

```{r code_block1}
# download pumpkins data & move it too current r directory
pumpkins = read.csv('pumpkins.csv', header = TRUE)
```

## Converting weights

Write a **function** to alter the weight in pounds to kg. Demonstrate the code below. Then convert the weight and create **a new** column called `weight_kg`

```{r weight_kg}
new.col = sapply(pumpkins$weight_lbs, function(s){
  s=s*0.4535924
})
pumpkins$weight_kgs = new.col
```


## A pumpkin plot

Here I want you to plot the relationship between the actual weight and the estimated weight. Both axes have to be in the same units - it is up to you whether it is lbs or kg but remember to write some text explaining this.

```{r}
ggplot(pumpkins, aes(weight_kgs, est_weight))+geom_point()

```


**Also** explain what the plot shows and whether there are outliers

```{r}
#plot shows that estimated weight is positively correlated with actual weight, two major outliers exist
```


## Some pumpkin queries

Which pumpkin is the heaviest? Where was it grown and in what year? Show the code below and make sure you return **only the top hit** - nb. `print(n = 1)` will help here.

```{r}
pumpkins %>% group_by(weight_kgs, id) %>% arrange(desc(weight_kgs)) %>% print(n=1)
```


## Pumpkins in the US and UK

Filter your dataset to include only pumpkins from the UK and US. The code below is intended as a hint:

```{r code_block2, echo = TRUE, eval = F}

pumpkins %>% filter(country == "United Kingdom" | country == "United States")
```

Now draw a `ggplot2` boxplot of the weight distributions in the two countries - which country tends to have heavier pumpkins?

```{r}
pumpkins %>% filter(country == "United Kingdom" | country == "United States") %>% ggplot(aes(country, weight_lbs, fill=country)) + geom_boxplot()
```

```{r}
#this is a github version control test
```

